\textsf{Are large language models superhuman chemists?}

### 2024-10-21 src/tex/ms.tex
minore cleanup

%\input{sections/manually_sources_table.tex}

>>>>

\begin{table}
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}
